Plant-pollintor networks worldwide are composed by the same specific building

### 2021-08-17 Draft/Draft.Rmd
overall motif patterns results

**Meso-scale analysis**

*Over- and under-represented motifs*

@@

*Over and under-represented functional groups on motif positions*

@@

*Over- and under-represented funtional group combinations of motifs*

@@

The hierarchical cluster analysis divided the dataset into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**): cluster 1 (selfing herbs) consisted on herbs with hermaphrodite flowers with high levels of autonomous selfing; cluster 2 (small outcrossing perennials) had small perennial species with a mixed of life forms (trees shrubs and herbs) with outcrossing hermaphroditic flowers; cluster 3 (self-incompatible perennials with large flowers) comprised perennial species with a mixed of life forms and had large self-incompatible hermaphroditic flowers with high number of ovules; cluster 4 (tall plants with small unisexual flowers) had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding system with small flowers but the highest number of flowers per plant and inflorescences; finally, cluster 5 (short-lived outcrossers with long zygomorphic flowers) was dominated by small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.

In total, there were 1126 pollinator species and were divided into 9 different taxonomical groups. From highest to lowest number of interactions of the different functional groups with plants: bees (2256), non-syrphid Diptera (1768), syrphids (845), Lepidoptera (437), Coleoptera (432), non-bee Hymenoptera (362), lizards (105), birds (80) and other insects (40).

>>>>

@@

**Over and under-represented functional groups on motif positions**

@@

**Over- and under-represented funtional group combinations of motifs**

@@

The hierarchical cluster analysis divided the dataset into five different clusters with different and overlapping characteristics (**Figure S3** and **Figure S4**): cluster 1 referred to as 'selfing herbs' consisted on herbs with hermaphroditic flowers with high levels of autonomous selfing; cluster 2 or 'small outcrossing perennials' had small perennial species with a mixed of life forms (trees shrubs and herbs) with outcrossing hermaphroditic flowers; cluster 3 referred to as 'self-incompatible perennials with large flowers' comprised perennial species with a mixed of life forms and large self-incompatible hermaphroditic flowers with high number of ovules; cluster 4 or 'tall plants with small unisexual flowers' had the tallest species, highest proportion of shrub and tree life forms, dioecious and monoecious breeding systems with small flowers but the highest numbers of flowers and inflorescences per plant; finally, cluster 5  referred to as 'short-lived outcrossers with long zygomorphic flowers' consisted on small perennial and short-lived herbs with long self-compatible zygomorphic flowers that were unable to self-pollinate.

In total, there were 1126 species of floral visitor with 6325 interactions recorded with plants. We divided them into 9 different taxonomical groups: bees with 2256 interactions with plants, non-syrphid Diptera with 1768 interactions, syrphids with 845 interactions, Lepidoptera with 437 interactions, Coleoptera with 432 interactions, non-bee Hymenoptera with 362 interactions and lizards, birds and other insects with a total of 225 interactions.
